Arc Blanc: a real time ocean simulation framework

### 2025-01-20 paper.tex
Change notation damping formulation

In the FDM simulation, \framework denotes by $h_{i,j}^n$ the water height $h(i\times \delta,j\times \delta,n \times dt)$ for discrete location $(i,j)\times \delta$ and time $n\times dt$.
This leads to the following explicit scheme:
\begin{equation}
	\label{eq:fdm_scheme}
	h_{i,j}^{n+1} = a\left(h_{i+1,j}^n+h_{i-1,j}^n+h_{i,j+1}^n+h_{i,j-1}^n-4h_{i,j}^n\right) + 2h_{i,j}^n - h_{i,j}^{n-1}
\end{equation}
where
\begin{equation}
	a=\frac{c^2dt^2}{\delta^2}.
\end{equation}
The Dirichlet boundary condition gives $h_{i,j}^n=0$ for $i$ or $j$ being on the boundary of $Z$.
Since a new wave is generated at each time step, a damping effect is added to make them disappear gradually.
Hence, the right part of Equation (\ref{eq:fdm_scheme}) is multiplied by the \textbf{damping factor} $d(t)=d^n$.
This damping factor is linearly related to the velocity of the mesh $v_M(t)$ to ensure numerical stability as follows:
\begin{equation}
	d(t) =
	\begin{cases}
		\left(1-\frac{||\mathbf{v_M}(t)||}{v_{max}}\right)d_0 + \frac{||\mathbf{v_M}(t)||}{v_{max}}d_{max} & \text{for~~}||\mathbf{v_M}(t)||\leq v_{max}, \\
		d_{max}                                                                          & \text{else}
	\end{cases}
\end{equation}
where $d_{max}$ is the maximum damping value obtained when the body's velocity is above a given threshold $v_{max}$,
and $d_0$ is the damping for a null velocity.
For a plausible appearance, \framework uses the following values by default:
\begin{equation}
	\begin{cases}
		d_0     & = 0.98,       \\
		d_{max} & = 0.999,      \\
		v_{max} & = 5 m.s^{-1}.
	\end{cases}
\end{equation}
Nevertheless, the user can adjust these values in a way that a body $M$ causes more or less interaction waves.

>>>>

In the FDM simulation, \framework denotes by $h_{i,j}^n$ the water height $h(i\times \delta,j\times \delta,n \times dt)$ for discrete location $(i,j)\times \delta$ and time $n\times dt$.
This leads to the following explicit scheme:
\begin{equation}
	\label{eq:fdm_scheme}
	h_{i,j}^{n+1} = a\left(h_{i+1,j}^n+h_{i-1,j}^n+h_{i,j+1}^n+h_{i,j-1}^n-4h_{i,j}^n\right) + 2h_{i,j}^n - h_{i,j}^{n-1}
\end{equation}
where
\begin{equation}
	a=\frac{c^2dt^2}{\delta^2}.
\end{equation}

The Dirichlet boundary condition gives $h_{i,j}^n=0$ for $i$ or $j$ being on the boundary of $Z$. Since a new wave is generated at each time step, a damping effect is added to make them disappear gradually. Hence, the right part of Equation (\ref{eq:fdm_scheme}) is multiplied by the \textbf{damping factor} $d(t) = d^n$.

This damping factor is linearly related to the velocity of the mesh $\mathbf{v_M}(t)$ to ensure numerical stability and is defined as:
\begin{equation*}
u = \text{clamp}\left(\frac{\|\mathbf{v_M}(t)\|}{v_{max}}, 0, 1\right),
\end{equation*}
\begin{equation}
d(t) = \text{lerp}(d_0, d_{max}, u),
\end{equation}
where:
\begin{itemize}
	\item $\text{clamp}(x, 0, 1)$ limits the value of $x$ to the range $[0, 1]$;
	\item $\text{lerp}(a, b, t) = (1-t)a + tb$ is the linear interpolation function;
	\item $v_{max}$ is the velocity threshold, above which the damping factor equals its maximum value $d_{max}$;
	\item $d_0$ is the damping value for a null velocity.
\end{itemize}

For a plausible appearance, \framework uses the following values by default:
\begin{equation}
	\begin{cases}
		d_0     & = 0.98,       \\
		d_{max} & = 0.999,      \\
		v_{max} & = 5 m.s^{-1}.
	\end{cases}
\end{equation}
Nevertheless, the user can adjust these values in a way that a body $M$ causes more or less interaction waves.
